### 2016-10-17 dissertation/normal.tex
dissertation part normal:rough finish

\begin{figure}[H]
\centering{
\includegraphics[width=5in]{newfig/Moore.eps}
\caption{A typical Moore machine and its state transition graph}
\label{fig:Moore}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=5in]{newfig/convention.eps}
\caption{Conventional verification techniques based on bit-level unrolling and equivalence checking}
\label{fig:convention}}
\end{figure}

@@

Basis $\{1,\alpha,\alpha^2,\alpha^3,\dots,\alpha^{k-1}\}$ is called {\bf standard basis} (StdB), which results in
a straightforward representation for elements, and operations of elements such as addition and subtraction.
The addition/subtraction of GF elements in StdB follows the rules of polynomial addition/subtraction
where coefficients belong to $\mathbb F_2$. In other words, using the definition of {\it exclusive or} in
Boolean algebra, element $A$ add/subtract by element $B$ in StdB is defined as
\begin{align}\label{eqn:StdB}
A+B = A-B &= (a_0,a_1,\dots,a_{k-1})_{StdB} \xor (b_0,b_1,\dots,b_{k-1})_{StdB} \nonumber\\
&=(a_0\oplus b_0, a_1\oplus b_1,\dots,a_{k-1}\oplus b_{k-1})_{StdB} 
\end{align}

@@

The $\lambda$-Matrix can be implemented with XOR and AND gates in circuit design.
The very naive implementation requires $O(C_N)$ gates, where $C_N$ is the number of
nonzero entries in $\lambda$-Matrix.
There usually exists multiple NBs in $\Fkk, k>3$. If we employ a random NB, there is no mathematical
guarantee that $C_N \sim o(k)$ (symbol $o$ denotes ``strictly lower than bound"). However,
Mullin et al. \cite{mullinONB} % This citation is valid
proves that in certain GF $\mathbb F_{p^{k_{opt}}}$, there always exists at least one NB such that 
its corresponding $\lambda$-Matrix has $C_N = 2n-1$ nonzero entries. A basis with this property is
called optimal normal basis (ONB), details are introduced in appendix.

@@

On the other hand, operands $A$ and $B$ can be written in NB as
$$A = (0010~1001)_{NB},~~B = (0100~0010)_{NB}$$
The $\lambda$-Matrix for $\mathbb F_{2}[x] \pmod{x^8+x^7+x^6+x^4+x^2+x+1}$
is
(Computation of $\lambda$-Matrix refers to appendix)
\begin{equation*}
M^{(0)} = \left(\begin{array}{lccccccr}
0 &0 &0 &0 &1 &0 &1 &1 \\
0 &0 &1 &1 &1 &1 &0 &0 \\
0 &1 &0 &0 &0 &0 &1 &0 \\
0 &1 &0 &0 &1 &1 &0 &1 \\
1 &1 &0 &1 &0 &1 &0 &0 \\
0 &1 &0 &1 &1 &0 &0 &1 \\
1 &0 &1 &0 &0 &0 &0 &0 \\
1 &0 &0 &1 &0 &1 &0 &1
\end{array}\right)
\end{equation*}
Taking matrix multiplication $c_0 = A\times M^{(0)}\times B^T$,
the result is $c_0 = 1$. Then by cyclic shifting $A$ and $B$
(or shifting $M^{(0)}$, either is applicable), we can successively
obtain other bits of product. The final answer is
$$C = (0000~0001)_{NB}$$
It is equivalent to the result in StdB.
\end{Example}

@@

It is a known fact that M-table $T$ can be converted from $\lambda$-Matrix $M$:
$$M_{i,j}^{(0)} = T_{j-i,-i}$$
with indices reduced modulo $k$. Thus we can write down the M-table of $\mathbb F_{2^5}$ with current NB $N$:

@@

\subsection{Customized Galois Field for Optimal Normal Basis Multiplier Design}

>>>>

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/Moore.eps}
\caption{A typical Moore machine and its state transition graph}
\label{fig:Moore}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/convention.eps}
\caption{Conventional verification techniques based on bit-level unrolling and equivalence checking}
\label{fig:convention}}
\end{figure}

@@

Basis $\{1,\alpha,\alpha^2,\alpha^3,\dots,\alpha^{k-1}\}$ is called {\bf standard basis} (StdB), which results in
a straightforward representation for elements, and operations of elements such as addition and subtraction.
The addition/subtraction of GF elements in StdB follows the rules of polynomial addition/subtraction
where coefficients belong to $\mathbb F_2$. In other words, using the definition of {\it exclusive or} (XOR) in
Boolean algebra, element $A$ add/subtract by element $B$ in StdB is defined as
\begin{align}\label{eqn:StdB}
A+B = A-B &= (a_0,a_1,\dots,a_{k-1})_{StdB} \xor (b_0,b_1,\dots,b_{k-1})_{StdB} \nonumber\\
&=(a_0\oplus b_0, a_1\oplus b_1,\dots,a_{k-1}\oplus b_{k-1})_{StdB} 
\end{align}

@@

The $\lambda$-Matrix can be implemented with XOR and AND gates in circuit design.
The very naive implementation requires $O(C_N)$ gates, where $C_N$ is the number of
nonzero entries in $\lambda$-Matrix.
There usually exists multiple NBs in $\Fkk, k>3$. If we employ a random NB, there is no mathematical
guarantee that $C_N \sim o(k)$ (symbol $o$ denotes ``strictly lower than bound"). However,
Mullin et al. \cite{mullinONB} % This citation is valid
proves that in certain GF $\mathbb F_{p^{k_{opt}}}$, there always exists at least one NB such that 
its corresponding $\lambda$-Matrix has $C_N = 2n-1$ nonzero entries. A basis with this property is
called optimal normal basis (ONB), details are introduced in appendix \ref{append:ONB}.

@@

On the other hand, operands $A$ and $B$ can be written in NB as
$$A = (0010~1001)_{NB},~~B = (0100~0010)_{NB}$$
The $\lambda$-Matrix for $\mathbb F_{2}[x] \pmod{x^8+x^7+x^6+x^4+x^2+x+1}$
is
(Computation of $\lambda$-Matrix refers to appendix \ref{append:NB})
\begin{equation*}
M^{(0)} = \left(\begin{array}{lccccccr}
0 &0 &0 &0 &1 &0 &1 &1 \\
0 &0 &1 &1 &1 &1 &0 &0 \\
0 &1 &0 &0 &0 &0 &1 &0 \\
0 &1 &0 &0 &1 &1 &0 &1 \\
1 &1 &0 &1 &0 &1 &0 &0 \\
0 &1 &0 &1 &1 &0 &0 &1 \\
1 &0 &1 &0 &0 &0 &0 &0 \\
1 &0 &0 &1 &0 &1 &0 &1
\end{array}\right)
\end{equation*}
Taking matrix multiplication $c_0 = A\times M^{(0)}\times B^T$,
the result is $c_0 = 1$. Then by cyclic shifting $A$ and $B$
(or shifting $M^{(0)}$, either is applicable), we can successively
obtain other bits of product. The final answer is
$$C = (0000~0001)_{NB}$$
It is equivalent to the result in StdB.
\end{Example}

@@

It is a known fact that M-table $T$ can be converted from $\lambda$-Matrix $M$:
$$M_{i,j}^{(0)} = T_{j-i,-i}$$
with indices reduced modulo $k$ (proof refers to appendix \ref{append:ONB}). Thus we can write down the M-table of $\mathbb F_{2^5}$ with current NB $N$:

@@

\section{Full-Blown Verification Procedure for Normal Basis Multiplier Functional Correctness Checking}
Once a gate-level design of a NB multiplier is generated, it is ready to be verified using 
similar approach appear in section \ref{sec:recha_approach}. The following part borrows contents
from my own conference paper \cite{myDATE}.
\subsection{Implicit Unrolling based on Abstraction with ATO}
In preliminaries we talk about the abstraction basics. If we use elimination term order 
$intermediate~variables~>~R~>~A,B$, the function of the combinational logic component 
can be abstracted as 
$$R = \Func(A,B)$$
If we are verifying the functional correctness of a combinational NB multiplier (e.g. Mastrovito multiplier
or Montgomery multiplier), the function given by abstraction will be $R=AB$.
While in the sequential case, the function of combinational logic only fulfills a part of the multiplication,
such as $F_{k-1}$ in equation \ref{eqn:aux}. Nevertheless, the abstraction still provides a word-level 
representation which works definitely better on unrolling than bit-level expressions.
In other words, with the assistance of abstraction, we can execute implicit unrolling instead of 
explicit unrolling and avoid bit-blasting problem.

For 2-input sequential NB multipliers, abstraction is utilized to implement following algorithm:
\vspace{-0.1in}
\IncMargin{1em}
\begin{algorithm}[hbt]
\SetAlgoNoLine
\LinesNumbered
 \KwIn{Circuit polynomial ideal $J$, vanishing ideal $J_0$, initial
   state ideal $R (=0), \mathcal{G}(A_{init}), \mathcal{H}(B_{init})$}

  $from_0(R,A,B) = \langle R, \mathcal{G}(A_{init}), \mathcal{H}(B_{init})\rangle$\;
  $i = 0$\;
  \Repeat{$i == k$}
  {
  	$i \gets i + 1$\;
%	$to^i(R',A',B') \gets$  $GB( \langle J_{ckt}, J_0,
%    from^{i-1}(R,A,B)\rangle )$ with abstraction term order\;
	$G \gets$GB$( \langle J + J_0+ from_{i-1}(R,A,B) \rangle
    )$ with ATO\;
	$to_i(R',A',B')\gets G\cap \mathbb F_{2^k}[R',A',B',R,A,B]$\;
	$from_i \gets to_i(\{R,A,B\}\setminus \{R',A',B'\})$\;
  }
\Return{$from_k(R_{final})$}
\caption {Abstraction via implicit unrolling for Sequential GF circuit
  verification}
\label{alg:modified}
\end{algorithm}
\DecMargin{1em}
\vspace{-0.1in}

\begin{figure}[H]
\centering{
\includegraphics[width=5in]{newfig/gf_seq_model.eps}
\caption{A typical normal basis GF sequential circuit model. $A =
  (a_0,\dots,a_{k-1})$ and similarly $B, R$ are $k$-bit registers;
  $A', B', R'$ denote next-state inputs.}
\label{fig:sequential}}
\end{figure}

We follow  the sequential GF circuit model of
figure \ref{fig:sequential}, with word-level variables $A, B, R$
denoting {\it present states (PS)} and $A', B', R'$ denoting {\it next
  states (NS)} of the machine; where $A = \sum_{i=0}^{k-1} a_i \beta^{2^i}$
for the PS variables and $A' = \sum_{i=0}^{k-1} a_i'
\beta^{2^i}$ for NS variables, and so on.  Variables $R\ (R')$ correspond to those that 
store the result, and $A, B\ (A', B')$ store input operands. E.g.,
for a GF multiplier, $A_{init}, B_{init}$ (and $R_{init} =
0$) are the initial values (operands) loaded into the registers,  and
$R = \Func(A_{init}, B_{init}) = A_{init} \times B_{init}$ is the final
result after $k$-cycles. Our approach aims to find this polynomial
representation for $R$.

Each gate in the combinational logic is represented by a Boolean
polynomial. To 
this set of Boolean polynomials, we append the polynomials that define
the word-level to bit-level relations for PS and NS variables ($A =
\sum_{i=0}^{k-1} a_i \beta^{2^i}$). We denote this set of polynomials
as ideal $J = \langle 
f_1, \dots, f_s \rangle \subset \Fkk[x_1, \dots, x_d, R, R', A, A', B,
  B']$, where $x_1, \dots, x_d$ denote the bit-level (Boolean) variables
  of the circuit. The ideal of vanishing polynomials $J_0$ is also included, and
then the implicit FSM unrolling problem is setup for abstraction.

The configurations of the flip-flops are the states of the
machine. Since the set of states is a finite set of points, we
can consider it as the variety of an ideal related to the circuit.
Moreover, since we are interested in
the function encoded by the state variables (over $k$-time
frames), we can project this variety on the word-level state
variables, starting from the initial state $A_{init}, B_{init}$.
Projection of varieties (geometry) corresponds to elimination ideals
(algebra), and can be analyzed via \Grobner bases. Therefore, we
employ a \Grobner basis computation with ATO: we use a {\it lex term
  order} with {\it bit-level variables} 
$>$ {\it word-level NS outputs} $>$ {\it word-level PS inputs}. This
allows to eliminate all the bit-level variables 
%(corresponding to the combinational logic and the state variables),
%so as to 
and derives a representation only in terms of words. 
Consequently, $k$-successive \Grobner basis computations implicitly
unroll the machine, and provide word-level algebraic $k$-cycle
abstraction for $R'$ as $R' = \F(A_{init}, B_{init})$.

Algorithm
\ref{alg:modified} describes our approach.  In the algorithm, $from_i$
and $to_i$ are polynomial ideals whose varieties are the valuations of
word-level variables $R, A, B$ and $R',A',B'$ in the $i$-th iteration;
and the notation ``$\setminus$'' signifies that the $NS$ in iteration
$(i)$ becomes the $PS$ in iteration $(i+1)$. Line 5 computes the Gr\"obner 
basis with the abstraction term order.  Line 6 computes the elimination 
ideal, eliminating the bit-level variables and representing the set of 
reachable states up to iteration $i$ in terms of the elimination ideal. 
These computations are analogous to those of image computations performed in FSM reachability. 
\begin{Example}[Functional verification of 5-bit RH-SMPO]
\label{ex:RHSMPO}
Figure \ref{fig:5bitRH} shows the detailed structure of a 5-bit RH-SMPO. The transition function for
operands $A,B$ is doing cyclic shift, while transition function for $R$ has to be computed through Gr\"obner basis
abstraction approach. Following ideal $J_{ckt}$ from line 5 in algorithm \ref{alg:modified} is the ideal for 
all gates in combinational logic block and definition of word-level variables.
\begin{align}
J_{ckt} = & d_0+a_4b_4, c_1+a_0+a_4, c_2+b_0+b_4, d_1+c_1c_2, c_3+a_1a_4,\nonumber\\
& c_4+b_1b_4, d_2+c_3c_4, e_0+d_0+d_1, e_3+d_1+d_2, e_4+d_2, \nonumber\\
& R_0+r_4+e_0, R_1+r_0, R_2+r_1, R_3+r_2+e_3, R_4+r_3+e_4,\nonumber\\
& A+a_0\alpha^5+a_1\alpha^{10}+a_2\alpha^{20}+a_3\alpha^9+a_4\alpha^{18},\nonumber\\
		 & B+b_0\alpha^5+b_1\alpha^{10}+b_2\alpha^{20}+b_3\alpha^9+b_4\alpha^{18},\nonumber\\
		 & R'+r_0'\alpha^5+r_1'\alpha^{10}+r_2'\alpha^{20}+r_3'\alpha^9+r_4'\alpha^{18},\nonumber\\
		 & R+R_0\alpha^5+R_1\alpha^{10}+R_2\alpha^{20}+R_3\alpha^9+R_4\alpha^{18};\nonumber
\end{align}
In our implementation here, since we only focus on the output variable $R$, evaluations of intermediate input 
operands $A, B$ are unnecessary. Polynomials about $A$ and $B$ can be removed from $J_{ckt}$, and $R$ is directly
evaluated by initial operands $A_{init}$ and $B_{init}$, which are associated with present state bit-level inputs
$a_0,a_1,\dots,a_4$ and $b_0,b_1,\dots,b_4$ by polynomials in $from^i$.

According to line 5 of algorithm \ref{alg:modified}, we merge $J_{ckt}$, $J_0$ and $from^i$, then compute its
Gr\"obner basis with abstraction term order (copy details here). There is a polynomial in form of $R'+\Func(A_{init},B_{init})$,
which should be included by $to^{i+1}$. $to^{i+1}$ also exclude next state variable $A'$ and $B'$, instead we 
redefine $A_{init}$ and $B_{init}$ using next state bit-level variables $\{a_i', b_j'\}$. Next state Bit-level variables
$a_i' = a_{i-1\pmod k}, b_j' = b_{j-1\pmod k}$ according to definition of cyclic shift.

Line 7 in algorithm \ref{alg:modified} is implemented by replacing $R'$ with $R$, $\{a_i', b_j'\}$ with $\{a_i,b_j\}$.

All intermediate results for each clock cycle are listed below:
\begin{itemize}
\item Clock 1: ${\bf from^0} = \{R, A_{init}+a_0\alpha^5+a_1\alpha^{10}+a_2\alpha^{20}+a_3\alpha^9+a_4\alpha^{18},
B_{init}+b_0\alpha^5+b_1\alpha^{10}+b_2\alpha^{20}+b_3\alpha^9+b_4\alpha^{18}\}$, \\
	${\bf to^1} = \{R'+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^2) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^8 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^8 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^8 B_{init}^2+(\alpha^4+\alpha^2) A_{init}^8 B_{init}+(\alpha^4+\alpha^2) A_{init}^4 B_{init}^{16}+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^8+(\alpha^2) A_{init}^4 B_{init}^4+(\alpha^3+\alpha^2+\alpha+1) A_{init}^4 B_{init}^2+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^8+(\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^3+\alpha^2+\alpha) A_{init}^2 B_{init}^2+(\alpha^4+\alpha) A_{init}^2 B_{init}+(\alpha^4+\alpha^3+1) A_{init} B_{init}^{16}+(\alpha^4+\alpha^2) A_{init} B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init} B_{init}^4+(\alpha^4+\alpha) A_{init} B_{init}^2+(\alpha^3+\alpha+1) A_{init} B_{init},
	A_{init}+a_4'\alpha^5+a_0'\alpha^{10}+a_1'\alpha^{20}+a_2'\alpha^9+a_3'\alpha^{18},
B_{init}+b_4'\alpha^5+b_0'\alpha^{10}+b_1'\alpha^{20}+b_2'\alpha^9+b_3'\alpha^{18}\}$
\item Clock 2: ${\bf from^1} = \{R+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^2) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^8 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^8 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^8 B_{init}^2+(\alpha^4+\alpha^2) A_{init}^8 B_{init}+(\alpha^4+\alpha^2) A_{init}^4 B_{init}^{16}+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^8+(\alpha^2) A_{init}^4 B_{init}^4+(\alpha^3+\alpha^2+\alpha+1) A_{init}^4 B_{init}^2+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^8+(\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^3+\alpha^2+\alpha) A_{init}^2 B_{init}^2+(\alpha^4+\alpha) A_{init}^2 B_{init}+(\alpha^4+\alpha^3+1) A_{init} B_{init}^{16}+(\alpha^4+\alpha^2) A_{init} B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init} B_{init}^4+(\alpha^4+\alpha) A_{init} B_{init}^2+(\alpha^3+\alpha+1) A_{init} B_{init},
	A_{init}+a_4\alpha^5+a_0\alpha^{10}+a_1\alpha^{20}+a_2\alpha^9+a_3\alpha^{18},
B_{init}+b_4\alpha^5+b_0\alpha^{10}+b_1\alpha^{20}+b_2\alpha^9+b_3\alpha^{18}\}$, \\
${\bf to^2} = \{R'+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^8+(\alpha^2) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+1) A_{init}^8 B_{init}^{16}+(\alpha^4+\alpha^2) A_{init}^8 B_{init}^8+(\alpha^4) A_{init}^8 B_{init}^4+(\alpha^4+\alpha^3+1) A_{init}^8 B_{init}^2+(\alpha^3+1) A_{init}^8 B_{init}+(\alpha^2) A_{init}^4 B_{init}^{16}+(\alpha^4) A_{init}^4 B_{init}^8+(\alpha^4) A_{init}^4 B_{init}^4+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^2+(\alpha) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^4+\alpha^3+1) A_{init}^2 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^2) A_{init}^2 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}+(\alpha^3+1) A_{init} B_{init}^8+(\alpha) A_{init} B_{init}^4+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init},
A_{init}+a_3'\alpha^5+a_4'\alpha^{10}+a_0'\alpha^{20}+a_1'\alpha^9+a_2'\alpha^{18},
B_{init}+b_3'\alpha^5+b_4'\alpha^{10}+b_0'\alpha^{20}+b_1'\alpha^9+b_2'\alpha^{18}\}$
\item Clock 3: ${\bf from^2} = \{R+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^8+(\alpha^2) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+1) A_{init}^8 B_{init}^{16}+(\alpha^4+\alpha^2) A_{init}^8 B_{init}^8+(\alpha^4) A_{init}^8 B_{init}^4+(\alpha^4+\alpha^3+1) A_{init}^8 B_{init}^2+(\alpha^3+1) A_{init}^8 B_{init}+(\alpha^2) A_{init}^4 B_{init}^{16}+(\alpha^4) A_{init}^4 B_{init}^8+(\alpha^4) A_{init}^4 B_{init}^4+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^2+(\alpha) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^4+\alpha^3+1) A_{init}^2 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^2) A_{init}^2 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}+(\alpha^3+1) A_{init} B_{init}^8+(\alpha) A_{init} B_{init}^4+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init},
A_{init}+a_3\alpha^5+a_4\alpha^{10}+a_0\alpha^{20}+a_1\alpha^9+a_2\alpha^{18},
B_{init}+b_3\alpha^5+b_4\alpha^{10}+b_0\alpha^{20}+b_1\alpha^9+b_2\alpha^{18}\}$, \\
${\bf to^3} = \{R'+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^{16}+(\alpha) A_{init}^{16} B_{init}^8+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^{16} B_{init}^4+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^{16} B_{init}+(\alpha) A_{init}^8 B_{init}^{16}+(\alpha+1) A_{init}^8 B_{init}^8+(\alpha^4) A_{init}^8 B_{init}^4+(\alpha^3+\alpha^2+1) A_{init}^8 B_{init}^2+(\alpha^4+\alpha^3+\alpha+1) A_{init}^8 B_{init}+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^4 B_{init}^{16}+(\alpha^4) A_{init}^4 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^4 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^4 B_{init}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}^{16}+(\alpha^3+\alpha^2+1) A_{init}^2 B_{init}^8+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+1) A_{init} B_{init}^{16}+(\alpha^4+\alpha^3+\alpha+1) A_{init} B_{init}^8+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init}^4+(\alpha^4+\alpha) A_{init} B_{init},
A_{init}+a_2'\alpha^5+a_3'\alpha^{10}+a_4'\alpha^{20}+a_0'\alpha^9+a_1'\alpha^{18},
B_{init}+b_2'\alpha^5+b_3'\alpha^{10}+b_4'\alpha^{20}+b_0'\alpha^9+b_1'\alpha^{18}\}$
\item Clock 4: ${\bf from^3} = \{R+(\alpha^4+\alpha^3+1) A_{init}^{16} B_{init}^{16}+(\alpha) A_{init}^{16} B_{init}^8+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^{16} B_{init}^4+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^{16} B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^{16} B_{init}+(\alpha) A_{init}^8 B_{init}^{16}+(\alpha+1) A_{init}^8 B_{init}^8+(\alpha^4) A_{init}^8 B_{init}^4+(\alpha^3+\alpha^2+1) A_{init}^8 B_{init}^2+(\alpha^4+\alpha^3+\alpha+1) A_{init}^8 B_{init}+(\alpha^4+\alpha^3+\alpha^2+1) A_{init}^4 B_{init}^{16}+(\alpha^4) A_{init}^4 B_{init}^8+(\alpha^4+\alpha^3+\alpha+1) A_{init}^4 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^4 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^4 B_{init}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^2 B_{init}^{16}+(\alpha^3+\alpha^2+1) A_{init}^2 B_{init}^8+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^4+(\alpha^3+\alpha+1) A_{init}^2 B_{init}^2+(\alpha^4+\alpha^3+\alpha^2+1) A_{init} B_{init}^{16}+(\alpha^4+\alpha^3+\alpha+1) A_{init} B_{init}^8+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init} B_{init}^4+(\alpha^4+\alpha) A_{init} B_{init},
A_{init}+a_2\alpha^5+a_3\alpha^{10}+a_4\alpha^{20}+a_0\alpha^9+a_1\alpha^{18},
B_{init}+b_2\alpha^5+b_3\alpha^{10}+b_4\alpha^{20}+b_0\alpha^9+b_1\alpha^{18}\}$, \\
${\bf to^4} = \{R'+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^{16} B_{init}^8+(\alpha^4+\alpha) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^8 B_{init}^{16}+(\alpha^3+1) A_{init}^8 B_{init}^8+(\alpha^4+\alpha^2+\alpha) A_{init}^8 B_{init}^4+(\alpha^2+\alpha) A_{init}^8 B_{init}^2+(\alpha^3+\alpha^2+1) A_{init}^8 B_{init}+(\alpha^4+\alpha) A_{init}^4 B_{init}^{16}+(\alpha^4+\alpha^2+\alpha) A_{init}^4 B_{init}^8+(\alpha^4+\alpha^2+\alpha) A_{init}^4 B_{init}^4+(\alpha^2+\alpha) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^2+\alpha) A_{init}^2 B_{init}^8+(\alpha^4+\alpha^2) A_{init}^2 B_{init}^2+(\alpha^3+\alpha^2+1) A_{init}^2 B_{init}+(\alpha^3+\alpha+1) A_{init} B_{init}^{16}+(\alpha^3+\alpha^2+1) A_{init} B_{init}^8+(\alpha^2+\alpha) A_{init} B_{init}^4+(\alpha^3+\alpha^2+1) A_{init} B_{init}^2+(\alpha) A_{init} B_{init},
A_{init}+a_1'\alpha^5+a_2'\alpha^{10}+a_3'\alpha^{20}+a_4'\alpha^9+a_0'\alpha^{18},
B_{init}+b_1'\alpha^5+b_2'\alpha^{10}+b_3'\alpha^{20}+b_4'\alpha^9+b_0'\alpha^{18}\}$
\item Clock 5: ${\bf from^4} = \{R+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}^{16}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^{16} B_{init}^8+(\alpha^4+\alpha) A_{init}^{16} B_{init}^4+(\alpha^3+1) A_{init}^{16} B_{init}^2+(\alpha^3+\alpha+1) A_{init}^{16} B_{init}+(\alpha^4+\alpha^3+\alpha^2+\alpha+1) A_{init}^8 B_{init}^{16}+(\alpha^3+1) A_{init}^8 B_{init}^8+(\alpha^4+\alpha^2+\alpha) A_{init}^8 B_{init}^4+(\alpha^2+\alpha) A_{init}^8 B_{init}^2+(\alpha^3+\alpha^2+1) A_{init}^8 B_{init}+(\alpha^4+\alpha) A_{init}^4 B_{init}^{16}+(\alpha^4+\alpha^2+\alpha) A_{init}^4 B_{init}^8+(\alpha^4+\alpha^2+\alpha) A_{init}^4 B_{init}^4+(\alpha^2+\alpha) A_{init}^4 B_{init}+(\alpha^3+1) A_{init}^2 B_{init}^{16}+(\alpha^2+\alpha) A_{init}^2 B_{init}^8+(\alpha^4+\alpha^2) A_{init}^2 B_{init}^2+(\alpha^3+\alpha^2+1) A_{init}^2 B_{init}+(\alpha^3+\alpha+1) A_{init} B_{init}^{16}+(\alpha^3+\alpha^2+1) A_{init} B_{init}^8+(\alpha^2+\alpha) A_{init} B_{init}^4+(\alpha^3+\alpha^2+1) A_{init} B_{init}^2+(\alpha) A_{init} B_{init},
A_{init}+a_1\alpha^5+a_2\alpha^{10}+a_3\alpha^{20}+a_4\alpha^9+a_0\alpha^{18},
B_{init}+b_1\alpha^5+b_2\alpha^{10}+b_3\alpha^{20}+b_4\alpha^9+b_0\alpha^{18}\}$, \\
${\bf to^5} = \{{\bf R'+A_{init}B_{init}},
A_{init}+a_0'\alpha^5+a_1'\alpha^{10}+a_2'\alpha^{20}+a_3'\alpha^9+a_4'\alpha^{18},
B_{init}+b_0'\alpha^5+b_1'\alpha^{10}+b_2'\alpha^{20}+b_3'\alpha^9+b_4'\alpha^{18}\}$
\end{itemize}
The final result is
$from^5(R_{final}) = R_{final}+A_{init}\cdot B_{init}$
\end{Example}
\subsection{Overcome Computational Complexity using RATO}
Similar to our improvements in section \ref{sec:reachaRATO}, RATO \cite{TimDAC} is also available to 
accelerate the GB computation here. More specifically, we obviate GB computation by turning it 
into a single-step multivariate polynomial division: first, in ideal generated by
gates information polynomials and word-level variable definition polynomials, find the unique pair of polynomial
generators with leading monomials not relatively prime to each other; then, compute their specification polynomial
using definition 
$$Spoly(f_w,f_g) = \frac{LCM}{lt(f_w)}\cdot f_w - \frac{LCM}{lt(f_g)}\cdot f_g$$
where $LCM$ is least common multiple of $lm(f_w)$ and $lm(f_g)$, and $lt$ denotes the leading term;
last, reduce $Spoly$ with ideal $J_{ckt}+J_0$, it is possible that the remainder will be canonical polynomial
function of the circuit. We will illustrate the whole improved procedure by applying RATO on 
5-bit RH-SMPO in figure \ref{fig:5bitRH}.
